Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/manuscript/appendix.Rmd
tweaks to figure captions, themes, and sizes

@@

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old. Each dot represents the average position from one video within a given age range.", warning=F}

ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  # ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin) +
  guides(size = FALSE) +
  ggthemes::scale_color_solarized(name = "")  +
  ggthemes::scale_fill_solarized(name = "") 
```

@@

```{r det_perf_by_age, fig.width=6.5, fig.height=3.2, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}

@@

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')
```

```{r}
ggarrange(p1, p2, nrow=1)
```

@@

```{r density-op-fps, fig.width=6, fig.height=3}
load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

@@

```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

@@

```{r, include=F}
f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces") + theme_classic()

h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands") + theme_classic()

>>>>

theme_set(theme_classic())

@@

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 5-31 months of age. Each dot represents the average position from one video within a given age range.", warning=F}

ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  # ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin) +
  guides(size = FALSE) +
  ggthemes::scale_color_solarized(name = "")  +
  ggthemes::scale_fill_solarized(name = "") +
  theme(legend.position = c(0.8, 0.1))
```

@@

```{r det_perf_by_age, fig.width=6.5, fig.height=3.1, fig.cap="F-score of OpenPose hand and face detections in the gold sample by child and age. Size indicates number of detections age bin/child."}

@@

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')

@@

```{r density-op-fps, fig.width=6.5, fig.height=3.2, fig.cap="Density plot of the locations of false positives for OpenPose detections for faces (left) and hands (right) in the gold set."}
load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

@@

```{r activities_by_lo, fig.width=6.5, fig.height=3.2, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

@@

```{r, include=F}
f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces")

h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands")
